Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-16 ms.tex
more complete discussion of zero-point and residual Solar dipole removal

To incorporate information about the dust emission on the Wien side of its 
spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|, and at 
times by frequency as 3000 GHz. \verb|i100| has angular resolution of $6.1'$. 
%list other %important characteristics of i100 e.g. that it has been 
%zodi-corrected and relies on dirbe on scales larger than ???

@@

\subsection{CMB Removal}
The CMB is effectively imperceptible at 857 GHz, but can be noticed at a 
low level at 545 GHz, and is prominent at 217 GHz and 353 GHz relative 
to the diffuse Galactic emission we wish to characterize, especially at high
latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
from each of our Planck maps \citep{smica}, after appropriate unit conversions.

@@

\subsection{Correlation versus HI}
The raw \PLANCK~maps we have downloaded show offsets relative to HI, in the
sense that the FIR emission does not go to zero when HI emission goes to
zero. Since HI correlates linearly with far-IR emission in the diffuse ISM, 
when the optical depth is low and molecular effects are negligible, we modeled
far IR emission as a constant times HI emission, plus some offset. We then
subtracted the best-fit offset such that

>>>>

To incorporate information about the dust emission on the Wien side of its 
spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|, and at 
times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
$6.1'$. 
%list other %important characteristics of i100 e.g. that it has been 
%zodi-corrected and relies on dirbe on scales larger than ???

@@

\subsection{CMB Removal}
The CMB is effectively imperceptible at 857 GHz, but can be noticed at a 
low level at 545 GHz, and is prominent at 217 GHz and 353 GHz relative 
to the diffuse Galactic emission we wish to characterize, especially at high
latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
from each of the relevant \PLANCK~maps \citep{smica}, after appropriate unit conversions.

@@

\subsection{Zero-Point}
Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components. At each frequency, there can
exist an overall, constant offset that must be subtracted to set the
zero level of Galactic dust. Additionally, faint residuals 
of the Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, 
we have adopted the zero-point offsets of \cite{planckdust} Table 1, which 
were derived by correlating \PLANCK~857 GHz versus HI at low column density, 
and then by correlating the other Planck channels against the corrected 857 
GHz map. We have not altered the \verb|i100| zero-point in any way. We have
also removed the Solar dipole residual according to \cite{planckdust}, 
by subtracting a dipole pattern oriented toward $(l, b) = ()$ and scaled
according to their Table 1.

The offset and residual dipole parameters for \PLANCK~217 GHz were not 
available from \cite{planckdust} Table 1. In order to set the zero-point of 
Galactic emission in the 217 GHz map, we simultaneously fit the constant 
offset and residual dipole amplitude. Restricting to regions of low column 
density (HI $<$ 200 K km/s), we modeled the 217 GHz map as:

\begin{equation}
\mathcal{I}_{217, i} = a\mathcal{I}_{857, i} + b\mathcal{D}_{i} + c
\end{equation}

With $i$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{217}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the Planck 857 GHz map with zodiacal emission, compact 
sources, and constant offset removed, smoothed to $1^{\circ}$ resolution. 
$\mathcal{I}_{217}$ is the corresponding $1^{\circ}$ resolution Planck 217 GHz 
map with zodiacal emission and compact sources removed. $\mathcal{D}$ is a
scaling of the Solar dipole with unit amplitude. Because $\sim$18,000 pixels
satisfy the low HI cut, we have an overconstrained linear model with three
parameters: a, b, and c. $a$ represents the slope of Planck 217 GHz 
versus Planck 857 GHz assuming they are linearly correlated, and is not
of any importance to our downstream analysis. $b$ represents the scaling of 
the Solar dipole that makes the 857 GHz vs. 217 GHz correlation tightest, and 
$c$ represents the constant offset necessary to make the zero level of the 217 
GHz map consistent with that of the 857 GHz map. Performing a linear least
squares fit with uniform weights and iterative outlier rejection, we find 
$a=4.33\times10^{-5}\ K/(MJy/sr)$, $b=-1.40\times10^{-5}\ K$, and 
$c=8.12\times10^{-5}\ K$. Note that $b$ represents 0.42\% of the Solar dipole 
amplitude, which is within the calibration uncertainty of the 217 GHz band. 
Figure 1 shows scatterplots of the 857 GHz versus 217 GHz correlation before 
and after correcting for our best-fit offset and dipole residual. Not only is 
the improvement striking in this scatterplot, but the residual dipole also 
appears visually well-corrected in the 217 GHz map itself.
